Global patterns of forest autotrophic carbon fluxes

### 2020-02-21 manuscript/manuscript draft.Rmd
Update manuscript draft.Rmd

There was a significant interactive effect between MAT and MAP for GPP, BNPP~root~, BNPP~fine~ ~root~, ANPP, ANPP~woody~ ~stem~, and R~root~ (fig.3). There was a significant additive effect for R~auto~. NPP and ANPP~foliage~ showed no significant interactive or additive effect.  {**NEED SI TABLE GIVING FITTED COEFFICIENTS & STATS**}

For the variables which showed a significant interactive or additive effect between MAT and MAP, no other climate variable, in combination with MAT, significantly improved on that model.

>>>>

There was a significant interactive effect between MAT and MAP for NPP and ANPP~woody~ ~stem~ (fig.3). There was a significant additive effect for GPP, ANPP and autotrophic respiration. ANPP~foliage~, BNPP, BNPP~fine~ ~root~, and root respiration showed no significant interactive or additive effect (see table S4).

For the variables which showed a significant interactive or additive effect between MAT and MAP, no other climate variable, in combination with MAT, significantly improved on that model. {**need to confirm this given changes in MAT MAP results**}
